\chapter{Expected Results}\label{cap:expected-results}
\thispagestyle{empty}

	We now present the expected results of the Ph.D. First, we describe the main contributions of the proposed work in Section~\ref{sec:contributions}. Finally, in Section~\ref{sec:publications}, we present some of the leading journals (Table~\ref{tbl:journals}) in which the results obtained during the doctorate can be published and some of the main conferences related to the research areas involved in this plan (Table~\ref{tbl:conferences}).

	\section{Main Contributions of the Thesis}\label{sec:contributions}
	\thispagestyle{empty}

	The following contributions are expected in each of the previously mentioned steps with the development of the proposed work:

	\begin{enumerate}

	\item {\bf Geolocation inferences from passive analysis}: in this step, we expect to find if Internet Exchange Points can be used as powerful scalable vantage points to map and generate geolocation inferences, their strengths and limitations. Besides, the passive analysis can discover gaps in existing physical and measurements (e.g., BGP) infrastructures

	\item {\bf Geolocation inferences from hybrid approach}: we believe that correlating active measurements with passive analysis of data can improve the generation of geolocation knowledge. It can help the identification of connectivity between ASes varies in developing areas (e.g., Latin America) and across different parts of the world. Besides, a precise mapping of peering interconnections and topology elements can improve the efficiency of traffic delivery for ASes and enhance knowledge about topology redundancy.

	\item {\bf Extension to larger scenarios}: we expect to provide a methodology accurate, scalable and reproducible to improve the mapping of peering interconnections and topology elements by exploiting the characteristics of the Internet Exchange Points, introducing new datasets and validations. We hope that using several IXPs can improve the Internet cartography.
 
    \end{enumerate}

	It is also expected that during the development of this work there will be the participation of master and scientific initiation students, performing work related to the doctoral thesis proposed in this plan. The participation in the training of these student's knowledge is then considered as one of the possible contributions.

	\section{Publications}
	\label{sec:publications}

	The development of PhD activities will generate results which will be used as a basis for the writing of 2-3 articles for journals and congresses. Table~\ref{tbl:journals} presents some of the main journals in which the results obtained during the doctorate can be published, while Table~\ref{tbl:conferences} presents some of the leading conferences of the research areas involved in this plan.


	\begin{table}[htp]
	\centering
	\begin{tabularx}{\textwidth}{l | c | c}
	\hline
	{\bf Journal}                                           & {\bf Impact Factor} & \textbf{Qualis} \\ \hline
    \textit{Communications of the ACM}                        &      4.027        & A1 \\ \hline
	\textit{IEEE/ACM Transactions on Networking}              &      3.376        & A1 \\ \hline
	\textit{ACM CCR}                					      &      2.008        & B1 \\ \hline
	\textit{Elsevier Computer Networks}                       &      2.516        & A1 \\ \hline
	

	\end{tabularx}
	\caption{Journals related to PhD}
	\label{tbl:journals}
	\end{table}

	\begin{table}[htp]
	\centering
	\begin{tabularx}{\textwidth}{ l | c | c | c }
	\hline
	{\bf Conference} & {\bf Acceptance Rate} & \textbf{H-index} & \textbf{Qualis}      \\ 
	                          							  &  &  & \textbf{2016}        \\ \hline
	\textit{ACM Internet Measurements}                    &  24.7\% & 75 & A1          \\ 
	\textit{(IMC) Conference}   						  &         &    &             \\ \hline
	\textit{Network Traffic Measurement}                  &  39.2\% & -- & --          \\
	\textit{ and Analysis Conference (TMA)}               &         &    &             \\ \hline
	\textit{Passive and Active Network}                   &  40.8\% & -- & A2          \\
	\textit{ Measurement Conference (PAM)}                &         &    &             \\ \hline
	\textit{ACM Special Interest Group on Data}           &  18\%   & 67 & A1          \\
	\textit{Communication (SIGCOMM) Conference}           &         &    &             \\ \hline
	\textit{ACM International Conference on}              &  17.2\% & 35 & A1          \\
	\textit{emerging Networking EXperiments}	          &         &    &             \\
	\textit{and Technologies(CoNEXT)}                     &         &    &             \\ \hline
	\textit{USENIX Symposium on Networked}                &  15.4\% & 62 & A1          \\
	\textit{Systems Design and Implementation}            &         &    &             \\
	\textit{(NSDI)}             				          &         &    &             \\ \hline
	\textit{USENIX Security Symposium}                    &  19.1\% & 70 & --          \\ \hline
	

	\hline
	\end{tabularx}
	\caption{Conferences related to PhD}
	\label{tbl:conferences}
	\end{table}